Measuring Software Ticket Quality using Statistical Analysis

### 2018-04-17 paper/paper.tex
Complete introduction section

This paper outlines the standard template for an MSci submission.
In earlier years, MSci students at the School of Computing
Science,
University of Glasgow, were expected to produce a full-length
dissertation. Now, the requirement is for MSci students to
write a paper of up to 14 pages in length, using the supplied
\texttt{mpaper} \LaTeX style file.

The precise structure of an MSci paper is not mandated, but it should
probably cover in detail the following aspects of the project.
\begin{enumerate}
\item General description of the problem, motivation, relevance
\item Background information, possibly including a literature survey
\item Description of approach taken to solve the problem, including
  high-level design and lower-level implementation details as appropriate
\item Evaluation, qualitative or quantitative as appropriate
\item Conclusion, including scope for future work
\end{enumerate}

@@

\begin{table}
\begin{tabular}{l||c||p{2cm}}
\emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
RedHat \\ \hline
Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
your kernel? \\ \hline
Mac OS & 10.7 & For people with more money than sense \\ \hline
\end{tabular}
\caption{\label{tab-eg}Single column table of figures}
\end{table}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.3]{images/alice.pdf}
\end{center}
\caption{\label{fig-eg}An example figure stretching over two columns}
\end{figure*}

@@

>>>>

In the past decade, technology has drastically increased its influence on 
virtually every aspect of our society. Therefore, software projects have 
inherently become more complex and require increasing number of developers in
the team. Due to this, software engineers have created issue tracking systems,
a means of planning, managing and tracking work products in the form of 
\emph{software tickets} or \emph{issues}.

There are multiple platforms for providing such issue tracking systems, among which
the most popular are Jira \cite{jira} and Bugzilla \cite{bugzilla}. For both platforms,
the tickets are split into two main categories: feature requests (i.e. feature to be 
implemented into the system) and bug reports (i.e. issue encountered by an end user or
discovered by a developer in the codebase). Regardless of the type of ticket, they provide
various types of information that can be filled in by the reporter, including:
  \begin{itemize}
    \item summary - short description of the feature to be implemented/encountered bug;
    \item description - longer textual field which goes into more detail regarding the ticket;
    it can include various types of information, such as stack traces or steps to reproduce a bug;
    \item attachments - screenshots, snippets of code or configuration files that might help
    close the ticket faster;
    \item comments - each ticket can have any number of comments where the people interested in 
    it can talk about what might have caused the bug, how to fix it etc.
  \end{itemize}

Even though tickets provide such comprehensive information regarding a specific task, studies have shown 
that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.

Therefore, there is a need in the community to find the answer to what makes for a high quality, valuable software ticket 
that would improve the overall performance of the development team and, inherently, the company. As there are many 
fields in a ticket, the number of unanswered questions is rather large: do stack traces have an influence on the quality
of a ticket? What about attachments and whether a screenshot is more helpful than a snippet of code? Does a negative sentiment
drawn from comments increase or decrease the time taken to solve a bug? How does grammar correctness influence the 
communication friction?

In this research paper, we present and discuss our findings after running a statistical analysis 
on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
which we define as the \emph{metric of quality} (\emph{time-to-complete} represents the period of time between the creation 
and the closing of a ticket). There are multiple novel aspects brought by our study, among which is the fact that it is one of 
the very few studies that have tackled this issue using a quantitative rather than a qualitative approach (with a very 
large number of tickets analysed) and also that it uses state-of-the-art sentiment \cite{wilson2005recognizing} as well as 
grammar correctness analysis techniques \cite{wilson2005recognizing}. We believe that our results are valuable 
contributions to the research community and the database produced after the analysis can help further studies with 
analyzed and well-tested data.

@@

@@

% \begin{table}
% \begin{tabular}{l||c||p{2cm}}
% \emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
% Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
% RedHat \\ \hline
% Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
% your kernel? \\ \hline
% Mac OS & 10.7 & For people with more money than sense \\ \hline
% \end{tabular}
% \caption{\label{tab-eg}Single column table of figures}
% \end{table}

% \begin{figure*}
% \begin{center}
% \includegraphics[scale=0.3]{images/alice.pdf}
% \end{center}
% \caption{\label{fig-eg}An example figure stretching over two columns}
% \end{figure*}
